---
title: "group 12 CA pollution burden"
author: "Ridhima Chaudhuri and Kat Orellana"
date: "11/14/2021"
output: html_document
---

```{r setup, include = TRUE, warning = FALSE, message = FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
```

```{r}
library(tidyverse)
library(janitor)
library(here)
library(hexbin)
```

```{r}
ces <- read_csv(here("data", "ces3demographics.csv")) %>%
  janitor::clean_names()
```

```{r}
ggplot(data = ces, aes(x = white_percent, y = ces_3_0_score)) +
  geom_hex() + 
  scale_fill_gradient(low = "blue", high = "coral") +
  theme_minimal() +
  labs( x = "Percent White Population", y = "CalEnviroScreen 3.0 Score", title= "Relationship Between Percent White Population and CES 3.0 Score", subtitle = "Data from CEJA Green Zones Manager Tiffany Eng") 
```


 **Figure 1**: A comparison between percent white population and the CalEnviroScreen 3.0 Score. Pink values indicate a higher count of observations,  blue values indicate a lower count of observations. 
 
As the percent white population within a community increases, the CalEnviroScreen 3.0 score decreases. The CalEnviroScreen 3.0 score indicates higher cumulative pollution burdens, therefore communities with a higher percentage of white residents are less likely to experience high pollution burdens in comparison to communities with a lower percentage of white residents. 

**Data Citation**: California Office of Environmental Health Hazard Assessment, (2018). "CalEnviroScreen 3.0", California Environmental Protection Agency. https://data.ca.gov/dataset/calenviroscreen-3-0-results
